---
title: "Week 9, Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

$$reg\_chg = \beta_0 + \beta_1x_{treat} + \beta_2x_{pov_n, i} + \beta_3x_{treat*pov_n, i} + \epsilon_i$$

* Describe the population for which you are creating the model.

The population for which we are creating the model is every voter within the
country of Kenya.

* Fit the model and interpret the coefficients. Focus on the coefficient of the interaction term.

```{r sc1}

fit_mod <- stan_glm(reg_chg ~ treatment*poverty_n,
         data = week_9,
         refresh = 0)

print(fit_mod, digits = 4)

```


## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?

The main thing we need to consider is whether January in this coming year is 
very different from whenever this data was gathered.

* Describe the ideal Preceptor Table.

We would know reg_chg with or without the treatment for every community in 
Kenya.

* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.

```{r sc2}

new_obs = tibble(treatment = "local", poverty_n = -1.60835093)

pp <- posterior_predict(fit_mod, newdata = new_obs) %>%
  as_tibble() %>% 
  mutate_all(as.numeric) 

pp %>%
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100,
                   color = "white") +
  labs(title = "Posterior Predictive Distribution",
       subtitle = "Prediction if treatment was applied to polling station 007/001",
       x = "Change in voter registration",
       y = "Probability") +
  geom_vline(xintercept = 0.04, color = "red")
  
mean(pp$`1` > 0.04)

```

* Answer the President's question.

There is a 13.35% chance of an increase in registration of 4% if we were to give 
polling station 007/001 the local treatment in January.


## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 



